Concurrent, Parallel Garbage Collection in Linear Time

### 2016-06-01 finaletd/mainintroduction.tex
changes

The preliminaries ideas required to understand the thesis is presented in the chapter ~\ref{prelim}. The chapter ~\ref{prelim} introduces the abstract version of garbage collection problem, a brief literature review of garbage collectors in general, and in detail, it explains Brownbridge garbage collector and the reasons for its failure. The understanding of Brownbridge is essential for this thesis as our algorithms extend the approach. The chapter ~\ref{shared} contains the brief introduction of shared memory garbage collectors, related works of the particular class of garbage collectors used in shared memory systems. Shared memory single collector and multi-collector algorithms are described in the chapter ~\ref{shared}. Apart from describing the algorithm, the chapter also contains the proofs of safety and completeness with simulated experimental results. The chapter also proves the linearity in a number of operations to detect garbage. The chapter ~\ref{distributed} explains the overview of distributed garbage collection, existing algorithms and their issues. Single collector and multi-collector distributed garbage collector algorithms are explained in abstract and introduce a novel technique to prove termination of garbage collection, safety, completeness and time complexity using isolation property. The chapter also includes the pseudocode of the algorithm. The distributed garbage collector is a theoretical leap in solving the problem in with scalability and other guarantees mentioned. The chapter ~\ref{conc} captures the overall contributions of the thesis in broad view with possible future works.

>>>>

The preliminary ideas required to understand the thesis are presented in chapter ~\ref{prelim}. Chapter ~\ref{prelim} introduces the abstract version of the garbage collection problem, a brief literature review of garbage collectors in general, and in detail, it explains Brownbridge garbage collector and explains the failures of Brownbridge garbage collector. The understanding of Brownbridge is essential for this thesis as our algorithms correct and extend the approach. Chapter ~\ref{shared} contains a brief introduction of shared memory garbage collectors and related works of the particular class of garbage collectors used in shared memory systems. Shared memory single collector and multi-collector algorithms are described in chapter ~\ref{shared}. Apart from describing the algorithm, chapter also contains the proofs of safety and completeness with simulated experimental results. The chapter also proves the linearity in the number of operations to detect garbage. Chapter ~\ref{distributed} explains the overview of distributed garbage collection, existing algorithms and their issues. Single collector and multi-collector distributed garbage collector algorithms are explained in abstract and a novel technique is introduced to prove termination of garbage collection, safety, completeness and time complexity using the isolation property. The chapter also includes the pseudocode of the algorithm. The distributed garbage collector with scalability and other guarantees mentioned above is a theoretical leap. Chapter ~\ref{conc} captures the overall contributions of the thesis in broad view with possible future works.
